### 2015-11-18 section/1_under.tex
near the end of section 3 revision

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\label{fig:GCC46401}
\end{figure}

@@

@@

\subsubsection{Methodology}
\begin{table}[h!]
\small{
\centering
\begin{tabular}{@{\hspace{3pt}}l@{\hspace{3pt}}|@{\hspace{3pt}}c@{\hspace{3pt}}}
\hline
Application Suite Description (language) & \# Bugs \\
\hline                            
{\bf Apache Suite} 	 & 11\\
%\cline{1-1}
{HTTPD:	Web Server (C)	}& \\
{TomCat:  Web Application Server (Java)}& \\
{Ant:	Build management utility (Java)}& \\
%\hline
%JMeter	& Load test utility (Java) & \\
\hline                            
{\bf Chromium Suite} Google Chrome browser (C/C++) & 4\\
\hline
%\multicolumn{2}{|l|}
{\bf GCC Suite}  GCC \& G++ Compiler (C/C++)     & 8\\
\hline
{\bf Mozilla Suite}  & 12\\
%\cline{1-1}
{Firefox: Web Browser (C++, JavaScript)}& 	\\
{Thunderbird: Email Client (C++, JavaScript)}& \\
\hline
{\bf MySQL Suite}     & 10	\\
%\cline{1-1}
{Server: Database Server (C/C++)}&  	\\
%\cline{1}
{Connector: DB Client Libraries (C/C++/Java/.Net)} &  	\\
\hline
{\bf Total}	   & 45 \\
\hline
\end{tabular}
}
\caption{Applications and bugs used in the study}
\label{tab:app_bug}
\end{table}

@@

\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lccccccccccccc}
\hline
                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
\cmidrule{2-6}
\cmidrule{8-12}
                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
\hline
\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
\multicolumn{1}{l}{ {\bf 0*} Resultless}
&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
\multicolumn{1}{l}{{\bf 1*} Resultless}
&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
(S: conditionally skip the loop; C: change the data structure)
}
\label{tab:root}
\end{table*}

@@

\paragraph{Coverage}
Our taxonomy does cover all inefficient loops under study. 
Resultless loops are about as common as redundant loops
(24 vs. 21).
Intuitively, 0* loops, where no iteration produces any results,
are rare in mature software. In fact, no bugs in this
benchmark suite belong to this category.
All other root-cause sub-categories are well represented.

\paragraph{Actionability}
As demonstrated in Table \ref{tab:correlation}, 
the root-cause categories in our taxonomy are highly correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultless loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

>>>>

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\label{fig:GCC46401}
\end{figure}

@@

\input section/tab_root

\input section/tab_appbug

@@

\subsubsection{Methodology}

@@

@@

\paragraph{Coverage}
As shown in Table \ref{tab:root}, 
our taxonomy does cover all inefficient loops under study. 
Resultless loops are about as common as redundant loops
(24 vs. 21).
Intuitively, 0* loops, where no iteration produces any results,
are rare in mature software. In fact, no bugs in this
benchmark suite belong to this category.
All other root-cause sub-categories are well represented.

\paragraph{Actionability}
As demonstrated in Table \ref{tab:root}, 
the root-cause categories in our taxonomy are well correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultless loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

### 2015-11-18 section/3_redundancy.tex
update table 2 and figure 4
near the end of section 3 revision

\subsubsection{Design overview}
To check whether there is redundant computation across different iterations
of one loop instance or across different instances of one static loop, we need
to address several challenges.

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
  \caption{A cross-loop redundant bug in Apache}
  \label{fig:Apache34464}
\end{figure}

\emph{How to judge redundancy between two iterations/loop-instances?}
Given two iterations (or loop-instances) $i_1$ and $i_2$, since they have 
the same source code, 
a naive, yet expensive, solution is to record and compare the return value of
every memory read conducted by $i_1$ and $i_2$. Two better alternative
solutions are to record and compare only the values written by the
side-effect instructions, such as 
line 9 in Figure~\ref{fig:Mozilla477564},
or read by 
the source instructions\footnote{We define source instructions in a code
region $r$ as a set of memory-read instructions that side-effect
instructions in $r$ depend on and do not depend on any other instructions
inside $r$.}, 
such as source[i] at line 12 of Figure~\ref{fig:Apache34464}.

Among the the above two potential solutions, our design chooses the second one,
because it is
more informative for performance diagnosis 
to track the cause rather than the effect.

\emph{How to handle partial redundancy?}
In practice, redundant loops may be doing largely the same, but not exactly
the same, computation across iterations or loop instances. 
%It is also possible
%TODO define loop instance.
%that only some, instead of all, iterations in a loop are doing redundant
%computation. 
We will discuss how we handle this issue in Section \ref{sec:cal}.

\emph{How to lower the overhead of record-and-compare?}
Even if we only record and compare the values returned by source instructions
the run-time overhead and the log size
could still be large. We will use static analysis and run-time sampling
to lower this time and spatial
overhead 
(Section \ref{sec:inst} and \ref{sec:perf}).
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

\emph{How to provide the most suitable fix-strategy suggestion?}
Finally, as discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
memoization and batching are both common fix strategies for redundant loops.
To pick the right fix strategies,
extra analysis is conducted by \Tool and presented in 
Section \ref{sec:redundant_fix}.

\subsubsection{Identifying source instructions}
\label{sec:dependence}

Informally, we use static analysis to identify a set of 
memory-read instructions that the loop computation depends on. We refer
to these instructions as \textit{source} instructions. The values returned
from them at run-time will be tracked and compared to identify
redundant computation.

Specifically, we first identify side-effect instructions in the loop, as 
discussed in Section \ref{sec:s_workless}; we then conduct static slicing 
from these instructions, considering both control and data
dependency, to identify source instructions.

%TODO How do you handle constant values? I didn't get it.
Our slicing ends when it reaches either a local-variable read conducted
outside the loop or a heap/global-variable read anywhere in the program.
For the latter case, our slicing stops because tracking data-dependency
through heap/global variables is complicated in multi-threaded C/C++
programs. For the former case, 
not including local-variable reads inside the loop can help reduce the
amount of data that needs to be recorded. 
When there are function calls inside the loop,  
we conduct slicing for return values of callees and side-effect instructions
inside callees. 
%In order to reduce the number of memory read we need to record inside callees, 
%we calculate previous writes conducted to the same address for each local-structure read and local-array read. 
%Since local structures and local arrays are mainly used in the declared functions, 
%it is easy to know whether read or write conducted on them are applied to the same address. 
We omit encountered constant values through slicing, because constant values will not influence whether a loop or an iteration is redundant.

@@

The analysis for cross-iteration and cross-loop redundancy analysis is pretty
much the same. The only difference is that, if a memory read instruction 
$i$ in a loop depends on the value returned by instruction $j$ in an earlier
iteration, we stop tracing the dependence at $i$ and consider $i$ as a
source instruction for cross-iteration redundancy analysis, while we continue
the slicing for cross-loop redundancy analysis. 
For example, 
the instruction defining the value of \texttt{i} is the only side-effect instruction 
for the loop at line 12 of Figure~\ref{fig:Apache34464}. 
The source instructions calculated by cross-loop dependence analysis include 
memory read \texttt{source[i]} inside the loop, 
and three values defined outside the loop, 
which represent the initial value of \texttt{i}, the value of \texttt{max} and \texttt{first} respectively. 
In contrast, 
the source instructions calculated by cross-iteration dependence analysis 
include value \texttt{i} defined in previous iteration, 
memory read \texttt{source[i]}, 
and two values defined outside the loop (\texttt{max} and \texttt{first}).

@@

After identifying source instructions, we instrument them to record
what values they read from memory
at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
Our trace also includes some delimiters and meta information that allows
trace analysis to differentiate values recorded from different instructions, 
loop
iterations, loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy.

After collecting values returned by source instructions from every iteration
of one or multiple loop instances, we need to process the trace and decide
whether the loops under study contain cross-iteration redundancy or 
cross-loop redundancy. We will first present our high-level algorithms, followed
by the exact implementation in our prototype.

@@

Our answer to these two questions stick to one principle: there should be
sufficient amount of redundant computation to make a loop likely root-cause
for a user-perceived performance problem and to make itself worthwhile to
get optimized by the developers. Consequently,
for the first question, \Tool takes a strict 
definition --- only iterations that are doing exactly the same computation are
considered redundant. Since one iteration may not contain too much computation,
a weaker definition here may lead to many false positives. For the 
second question, we believe there should be a threshold. In our current 
prototype,
when the number of distinct iterations is less than half of the total iterations, 
we consider the loop to be cross-iteration redundant. 
%when the number of distinct iterations is less than half of the total iterations 
%iterations/(distinct iterations) = 2

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache37184.java}}
  \caption{A cross-iteration redundant bug in Apache}
  \label{fig:Apache37184}
\end{figure}

For example, Figure~\ref{fig:Apache37184} shows a loop from Apache-Ant that
contains cross-iteration redundancy.
Under the problem triggering input, there are
only few distinct listeners, and most of the
loop iterations in \texttt{fireMessageLoggedEvent}
are doing redundant work. 
%The problem for this bug is that developers say that the performance 
%loss happens in fireMessageLoggedEvent, but in the code I found, function
%messageLogged does not contain anything, and it is an empty function.
%I guess either developers do not have correct understanding of this bug,
%or I did not find the correct codes.

For cross-loop redundancy, we need to answer similar questions,
especially how to judge whether two loop instances are doing redundant work ---
should they contain exactly the same number of iterations and doing exactly
the same computation in each iteration?
%Second, is a (static) loop problematic when it contains two instances that
%are redundant with each other?

Our answers here are different from our answers above for cross-iteration
redundancy analysis.
We do not require two loop instances to
conduct exactly the same computation to be considered redundant. The rationale
is that a whole loop instance contains a lot of computation, much more than
one iteration in general. Even if only part of its computation
is redundant, it could still be the root-cause of a user-perceived performance
problem and worth developers' attention.

In fact, in practice, we almost have never seen cases where different loop 
instances are doing exactly the same computation.
For example, Figure~\ref{fig:Mozilla477564} demonstrates a cross-loop redundancy
problem in Mozilla. Here, the
latter instances contain more iterations than previous instances. 
Figure~\ref{fig:Apache34464} shows an example in Apache, 
The inner loop, which starts from line 9,  
searches from the beginning of a string \texttt{sb} for a target sub-string 
\texttt{s}. Since the outer loop, which starts on line 36, appends one 
character to \texttt{sb} in every iteration, every inner loop instance is 
doing computation that is similar, but not exactly the same, 
from its previous instance.

@@

The implementation of checking cross-iteration redundancy is straightforward.
We will record a sequence of $<InstID, Value>$ pair for every monitored
iteration, with each $InstID$ representing a unique source instruction.
We consider two iterations to be redundant, if their sequences are exactly the
same. To make sure a loop contains sufficient redundant computation, 
we calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
the total number of iterations in the loop by the number of distinct iterations.
The smaller the rate is, with 1 being the minimum possible value, 
the less cross-iteration redundancy the loop contains.

@@

The key of this implementation is
to judge whether two dynamic loop instances $l_1$ and $l_2$ 
are redundant or not.
The challenge is that $l_1$ and $l_2$ may have executed different number of
iterations; in different iteration, a different set of source instructions
may have executed. Therefore, we cannot simply merge values from different
source instructions and iterations together and compare two big data sequence.
Instead, we decide to check the redundancy for each source instruction across
$l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
all source instructions as the \textit{cross-loop redundancy rate} between
$l_1$ and $l_2$.

@@

\[
\Scale[0.8]{
	Redundancy(I) =  \frac{dist(SeqA,SeqB) - (len(SeqA) - len(SeqB))}{len(SeqB)}
}
\]

@@

\subsubsection{Dynamic performance optimization: sampling}
\label{sec:inst}

@@

Recording values returned by every source instructions would lead to 
huge run-time time. To lower the overhead,
we use random sampling to reduce the number of instructions that we
track at run time. Due to the repetitive nature of performance bugs,
we will still be able to recognize redundant 
computation as long as the sampling rate is not too sparse (we will evaluate
this in Section \ref{sec:experiment}). 
Our sampling scheme requires almost no changes to our redundancy 
identification algorithm discussed in Section \ref{sec:cal}.

@@

\paragraph{Cross-loop redundancy analysis} 
At high level, we randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediately next loop instance too.
The implementation is straightforward by cloning the whole loop and making
sampling decisions in the loop pre-headers.
%; (2)
%sampling is conducted when \texttt{CurrentID} equals either
%\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
%increased by a random value in the latter case.

@@

\subsubsection{Static analysis for performance optimization}
\label{sec:perf}

@@

For cross-iteration redundancy, batching is often used towards
batching I/O related operations, based on our empirical study. 
Therefore, we treat I/O related redundancy separately.
Specifically, when the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, we report this
as I/O related redundancy problem and suggest batching as a potential fix
strategy.

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper to use. \Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is updating 
an sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to help save much computation.

>>>>

\subsubsection{Design overview}
At high level, we will compare the computation of different iterations
from one loop instance and that of different loop instances from 
one static loop, 
and judge whether there exists redundancy.
Specifically, our design needs to answer several questions.

\emph{What to compare?}
Given two loop iterations (or loop instances) $c_1$ and $c_2$, since they 
originate from the same source code $C$, 
a naive approach is to record the value read by
every memory read instruction in $c_1$ and $c_2$. 
We will know whether $c_1$ and $c_2$ are redundant with each other by comparing
these values.
Of course, we could do better by checking fewer instructions, as
some of these values are determined by values read earlier in $c_1$ and/or 
$c_2$. Informally speaking, we only need to compare \textit{input}
values of $c_1$ and $c_2$ to decide whether they are redundant with each other. 
We will present our formal definition of \textit{input} values, and
how we identify and record them in
Section \ref{sec:dependence}.

%TODO
%Among the the above two potential solutions, our design chooses the second one,
%because it is
%more informative for performance diagnosis 
%to track the cause rather than the effect.

\emph{How to compare?}
Naively, we can judge two iterations or two
loop instances to be redundant with each other only when they read exactly
the same data and conduct exactly the same computation. However,
in practice, redundant loops may be doing largely, but not completely,
the same computation across iterations or loop instances. 
%It is also possible
%TODO define loop instance.
%that only some, instead of all, iterations in a loop are doing redundant
%computation. 
We will discuss how we handle this issue in Section \ref{sec:cal}.

\emph{How to lower the overhead of record-and-compare?}
We will use both static optimization and dynamic sampling
to reduce the amount of data that we need to record and compare, lowering
time and spatial overhead. Details will be presented in 
Section \ref{sec:inst} and \ref{sec:perf}.
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

\emph{How to suggest the most suitable fix strategy?}
As discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
memoization and batching are both common fix strategies for redundant loops.
To pick the right strategy,
extra analysis is conducted by \Tool and presented in 
Section \ref{sec:redundant_fix}.

\subsubsection{Identifying and recording \textit{inputs}}
\label{sec:dependence}

Informally, we use static analysis to identify a set of 
memory-read instructions that the computation of code $C$
depends on. We refer
to these instructions as \textit{input} instructions for $C$. 
The values returned
from them at run-time will be tracked and compared to identify
redundant computation among different instances of $C$.

Specifically, \Tool first identifies side-effect instructions in $C$.
%, as 
%discussed in Section \ref{sec:s_workless}. 
It then conducts 
backward static slicing 
from these instructions, considering both control and data
dependency. For every memory read instruction $r$ 
(\texttt{read(v)}) that static slicing encounters, \Tool checks whether $r$
satisfies either one of the following two conditions. 
If $r$ does, it is marked as
an \textit{input} instruction; otherwise, \Tool continues growing the
slice beyond $r$.
The two conditions are:
(1) the value of $v$ is defined outside $C$;
(2) $v$ is a heap or global variable.
The rationale for the first condition is that slicing outside $C$ is
unnecessary for redundancy judgement among instances of $C$.
The rationale for the second condition is that tracking data-dependency
through heap or global variables is complicated in multi-threaded C/C++
programs.

The analysis for cross-iteration and cross-loop redundancy analysis is similar
--- simply replacing $C$ in the above algorithm with one iteration or
the whole loop body.

%TODO sound or complete

Our analysis considers function calls inside $C$ --- slicing is conducted
for return values of callees and side-effect instructions
inside callees. 
%In order to reduce the number of memory read we need to record inside callees, 
%we calculate previous writes conducted to the same address for each local-structure read and local-array read. 
%Since local structures and local arrays are mainly used in the declared functions, 
%it is easy to know whether read or write conducted on them are applied to the same address. 
We omit encountered constant values through slicing, because constant values will not affect the redundancy judgement.

Note that another possible approach is to simply record and compare what
are written by the side-effect instructions in $C$.
We did not choose this approach because we believe it is not sufficient
to judge redundancy. Consider a loop that goes through a character array 
to check if there exists any special characters in the array
and returns a boolean
variable denoting its checking result. Running this loop on 
different arrays is not redundant, but could easily be judged as redundant
when only comparing the loop side-effect (e.g., always returning 
\texttt{FALSE}).

@@

%TODO why not directly judge side-effect values

\paragraph{Example}
Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache. 
It contains a cross-loop redundant bug --- 
the \texttt{for} loop starting on line 7 could be executed for many times,
applied to many \texttt{source} strings slightly different from each other
with a lot of
redundant computation.
Below, we use it to demonstrate how we identify \texttt{input}s.

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true,numbers=left}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
  \caption{A cross-loop redundant bug in Apache}
  \label{fig:Apache34464}
\end{figure}

Take the simple loop at line 10 of Figure~\ref{fig:Apache34464} as an example.
Its only side-effect is to update \texttt{i}.
For cross-loop redundancy analysis, we will consider the whole loop and 
identify these as \textit{input}s:
every \texttt{source[i]} read inside the loop;
the initial value of \texttt{i} defined outside the loop;
\texttt{max} defined outside the loop; 
and \texttt{first} defined outside the loop.
For cross-iteration redundancy analysis, the \textit{input}s for each
iteration is slightly different:
value \texttt{i} defined in previous iteration, 
the \texttt{source[i]} read in that iteration, 
and two values defined outside the loop, \texttt{max} and \texttt{first}.

Take the big loop at line 7 of Figure~\ref{fig:Apache34464} as an example.
The \textit{input}s for the whole loop include:
three values defined outside the loop
(\texttt{max}, \texttt{first}, \texttt{targetLen}) and every
\texttt{source[.]} and \texttt{target[.]} read inside the loop.
This set is already smaller than the set of all data read by the loop.
We will further shrink this set, removing invariant and others, 
in Section \ref{sec:perf}.

@@

After identifying \textit{inputs} using static analysis, 
\Tool then instruments the program to record \textit{inputs} values at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
The run-time trace will also include delimiters and meta information that allows
trace analysis to differentiate values recorded from different instructions, 
loop
iterations, loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy.

Once the trace under problematic workload is collected either during
off-line debugging or during production runs, 
\Tool will process the trace and decide
whether the loops under study contain cross-iteration redundancy or 
cross-loop redundancy. We will first present our high-level algorithms, followed
by the exact implementation in our prototype.

@@

Our answer to these two questions stick to one principle: there should be
sufficient amount of redundant computation to make a loop likely culprit
for a user-perceived performance problem and to make itself worthwhile to
get optimized by developers. Consequently,
for the first question, \Tool takes a strict 
definition --- only iterations that are doing exactly the same computation are
considered redundant. Since one iteration may not contain too much computation,
a weaker definition here may lead to many false positives. For the 
second question, we believe there should be a threshold. In our current 
prototype,
when the number of distinct iterations is less than half of the total iterations, 
we consider the loop to be cross-iteration redundant. 
%when the number of distinct iterations is less than half of the total iterations 
%iterations/(distinct iterations) = 2

\comment{
\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache37184.java}}
  \caption{A cross-iteration redundant bug in Apache}
  \label{fig:Apache37184}
\end{figure}

For example, Figure~\ref{fig:Apache37184} shows a loop from Apache-Ant that
contains cross-iteration redundancy.
Under the problem triggering input, there are
only few distinct listeners, and most of the
loop iterations in \texttt{fireMessageLoggedEvent}
are doing redundant work. 
%The problem for this bug is that developers say that the performance 
%loss happens in fireMessageLoggedEvent, but in the code I found, function
%messageLogged does not contain anything, and it is an empty function.
%I guess either developers do not have correct understanding of this bug,
%or I did not find the correct codes. 
}

For cross-loop redundancy, we need to answer similar questions.
How to judge whether two loop instances are doing redundant work ---
should they contain exactly the same number of iterations and doing exactly
the same computation in each iteration?
%Second, is a (static) loop problematic when it contains two instances that
%are redundant with each other?

Following the same principle discussed above, we have slightly different
answers here.
We do not require two loop instances to
conduct exactly the same computation to be considered redundant. The rationale
is that a whole loop instance contains a lot of computation, much more than
one iteration in general. Even if only part of its computation
is redundant, it could still be the root-cause of a user-perceived performance
problem and worth developers' attention.

In practice, we rarely see cases where different loop 
instances are doing exactly the same computation.
For example, Figure~\ref{fig:Mozilla477564} demonstrates a cross-loop redundancy
problem in Mozilla. Here, the
latter instances contain more iterations than previous instances. 
Figure~\ref{fig:Apache34464} shows an example in Apache, 
The inner loop, which starts from line 9,  
searches from the beginning of a string \texttt{sb} for a target sub-string 
\texttt{s}. Since the outer loop, which starts on line 36, appends one 
character to \texttt{sb} in every iteration, every inner loop instance is 
doing computation that is similar, but not exactly the same, 
from its previous instance.

@@

The implementation of checking cross-iteration redundancy is straightforward.
\comment{
We will record a sequence of $<InstID, Value>$ pair for every monitored
iteration, with each $InstID$ representing a unique source instruction.
We consider two iterations to be redundant, if their sequences are exactly the
same. To make sure a loop contains sufficient redundant computation, 
}
We calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
the total number of iterations in the loop by the number of distinct iterations.
The smaller the rate is, with 1 being the minimum possible value, 
the less cross-iteration redundancy the loop contains.

@@

The key of this implementation is
to judge whether two dynamic loop instances $l_1$ and $l_2$ 
are redundant or not.
The challenge is that $l_1$ and $l_2$ may have executed different numbers of
iterations; in different iterations, different sets of source instructions
may have executed. Therefore, we cannot simply chain values from different
input instructions and iterations together and compare two data sequences.
Instead, we decide to check the redundancy for each source instruction across
$l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
all source instructions as the \textit{cross-loop redundancy rate} between
$l_1$ and $l_2$.

@@

\[
\Scale[0.8]{
	Redundancy(I) =  \frac{dist(SeqA,SeqB) - (len(SeqA) - len(SeqB))}{len(SeqA)}
}
\]

@@

\subsubsection{Dynamic optimization (sampling)}
\label{sec:inst}

@@

Recording values returned by every source instruction would lead to 
huge run-time overhead. To lower the overhead,
we use random sampling to reduce the number of instructions that we
track at run time. Due to the repetitive nature of performance bugs,
we will still be able to recognize redundant 
computation as long as the sampling rate is not too sparse, which
we will evaluate
in Section \ref{sec:experiment}. 
Our sampling scheme requires almost no changes to our redundancy 
identification algorithm discussed in Section \ref{sec:cal}.

@@

\paragraph{Cross-loop redundancy analysis} 
We randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediate next loop instance too.
The implementation is straightforward by cloning the whole loop and making
sampling decisions in the loop pre-headers.
%; (2)
%sampling is conducted when \texttt{CurrentID} equals either
%\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
%increased by a random value in the latter case.

@@

\subsubsection{Static optimization}
\label{sec:perf}

@@

For cross-iteration redundancy, batching is often used for
I/O related operations.
Therefore, we treat I/O related redundancy separately.
Specifically, when the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, we report this
as I/O related redundancy problem and suggest batching as a potential fix
strategy.

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper to use. \Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is to update
a sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to help save much computation and
hence batching is suggested.
